\documentclass{letter}
\usepackage[top=0.5cm, bottom=0.5cm]{geometry}
\usepackage{xcolor}
\date{\today}

\newcommand{\master}{M.Sc. Mathematics}
\newcommand{\uni}{University of Bonn}
\newcommand{\city}{Bonn}

% \newcommand{\master}{M2 Applied and Theoretical Mathematics}
% \newcommand{\uni}{Paris Sciences et Lettres University}
% \newcommand{\city}{Paris}
\newcommand{\scholar}{DAAD grant}

%% for scholarship 
\begin{document}
\begin{letter}
  \hfill

  \opening{To whom it may concern,}
  \medskip

  My name is Víctor Ballester and I am currently enrolled in my last course in the Mathematics degree at the Autonomous University of Barcelona. For years I have been highly attracted to Applied Mathematics, and in particular, to dynamical systems and numerical analysis. This is one of the main reasons why I am applying for the \master\ at the \uni with the \scholar. Once finished the master, I would like to continue my studies in a doctoral program.

  There are two main reasons to apply for this master. Firstly, my current university studies have given me the insights to become familiar with concepts of analysis and the theory of differential equations. Subjects such as Differential Equations And Modelling (I and II), Numerical Methods and all courses of Analysis have given me the tools to properly understand how to deal with applied complex problems in many branches of science. Because of this, I find the relation that Math has with Physics and Engineering really interesting but without losing the rigor that makes Math so gorgeous. And as far as I am concerned, your master program does have a vast number of applied subjects. And this is something that really appeals to me.

  Secondly, applying for such an outstanding college with so prestigious professors is really challenging. But the fact that I have always dreamed of studying at this high level in a foreign country makes me feel motivated and enthusiastic about it. In addition to that, the experience that someone gets by living and studying abroad is very culture-enriching. Thus, I am very looking forward to moving to \city\ for a while.

  Regarding my performance in Math, I would like to mention that I have been improving not only my marks but also my deep knowledge in the subjects during my time at university. This is due to several reasons. First of all, I consider myself a very hard-working person as well as highly competitive in all aspects. These competences have given me the power to become better in many aspects of my life, specially in Math in which the fact of having bright classmates has encouraged me to do better in many subjects. On the other hand, the annual participation in many well-known Math and Physics competitions proves my absolute love for these subjects as well as the passion they transmit to myself. All of this academic background stands me in good stead to pursue higher studies abroad.


  On balance, the acceptance in this master would allow me to continue expanding my knowledge of Math more deeply at the so prestigious \uni.

  Thank you very much for considering my application.
  \bigskip

  Yours faithfully,

  Víctor Ballester

\end{letter}
\end{document}

% \begin{document}
% \begin{letter}
%   \hfill

%   \opening{To whom it may concern,}
%   \medskip

%   My name is Víctor Ballester and I am currently enrolled in my last course in the Mathematics degree at the Autonomous University of Barcelona. For years I have been highly attracted to Applied Mathematics, and in particular, to dynamical systems and numerical analysis. This is one of the main reasons why I am applying for the \master\ at the \uni. Once finished the master, I would like to continue my studies in a doctoral program.

%   There are two main reasons to apply for this master. Firstly, my current university studies have given me the insights to become familiar with concepts of analysis and the theory of differential equations. Subjects such as Differential Equations And Modelling (I and II), Numerical Methods and all courses of Analysis have given me the tools to properly understand how to deal with applied complex problems in many branches of science. Because of this, I find the relation that Math has with Physics and Engineering really interesting but without losing the rigor that makes Math so gorgeous. And as far as I am concerned, your master program does have a vast number of applied subjects. And this is something that really appeals to me.

%   Secondly, applying for such an outstanding college with so prestigious professors is really challenging. But the fact that I have always dreamed of studying at this high level in a foreign country makes me feel motivated and enthusiastic about it. In addition to that, the experience that someone gets by living and studying abroad is very culture-enriching. Thus, I am very looking forward to moving to \city\ for a while.

%   Regarding my performance in Math, I would like to mention that I have been improving not only my marks but also my deep knowledge in the subjects during my time at university. This is due to several reasons. First of all, I consider myself a very hard-working person as well as highly competitive in all aspects. These competences have given me the power to become better in many aspects of my life, specially in Math in which the fact of having bright classmates has encouraged me to do better in many subjects. On the other hand, the annual participation in many well-known Math and Physics competitions proves my absolute love for these subjects as well as the passion they transmit to myself. All of this academic background stands me in good stead to pursue higher studies abroad.


%   On balance, the acceptance in this master would allow me to continue expanding my knowledge of Math more deeply at the so prestigious \uni.

%   Thank you very much for considering my application.
%   \bigskip

%   Yours faithfully,

%   Víctor Ballester

% \end{letter}
% \end{document}


% RAFAEL DEL PINO

% I consider myself a very hard-working person. When I started my Mathematics degree I realized that that was the time to demonstrate what I could do. From that time on I have been consistently improving my grades: from an average grade of 8,71 on the first year to an average grade of 9,73 on the third year passing through a 9,30 on the second year. A part from my grades I love to help other students having difficulties to properly understand a taught concept that has been unclear in class. Thus, I usually spend quite a few hours per week discussing problems with classmates. And I sincerely consider this activity very worthy.

% Another aspect that characterizes me is consistency and determination on preset goals. Indeed, I will always make any possible effort to try to achieve my goals no matter how difficult could this be for me.