\documentclass{letter}
\usepackage[top=0.5cm, bottom=0.5cm]{geometry}
\usepackage{xcolor}
\date{\today}

% \newcommand{\master}{M.Sc. Mathematics}
% \newcommand{\uni}{University of Bonn}
% \newcommand{\city}{Bonn}
% \newcommand{\scholar}{DAAD grant}

\newcommand{\program}{Ph.D.\ position}
\newcommand{\uni}{University of Manchester}
\newcommand{\city}{UK}
% \newcommand{\scholar}{PSL grant}

%% for scholarship 
\begin{document}
\begin{letter}
  \hfill

  \opening{To whom it may concern,}
  \medskip

  % My name is Víctor Ballester and I am currently enrolled in my master degree M2 Applied and Theoretical Mathematics at Paris-Dauphine University. Last year I graduated from Mathematics at the Autonomous University of Barcelona. For years I have been highly attracted to Applied Mathematics, and in particular, to dynamical systems and numerical analysis. This last months I discovered the field of fluid dynamics, and I'm particulary interested in doing research regarding Aerodynamics, both from the theoretical and numerical point of view. This is one of the main reasons why I am applying for the \program\ at the \uni.

  % There are two main reasons to apply for this PhD. Firstly, my current university studies have given me the insights to become familiar with concepts of analysis and the theory of differential equations. Subjects such as Differential Equations And Modelling (I and II), Numerical Methods and all courses of Partial Differential Equations have given me the tools to properly understand how to deal with applied complex problems in many branches of science. Because of this, I find the relation that Math has with Physics and Engineering really interesting but without losing the rigor that makes Math so gorgeous.

  % Secondly, applying for such an outstanding college with so prestigious professors is really challenging. But the fact that I have always dreamed of doing research at this high level in a foreign country makes me feel motivated and enthusiastic about it. In addition to that, the experience that someone gets by living and studying abroad is very culture-enriching. Thus, I am very looking forward to moving to \city\ for a while.

  % Regarding my performance in Math, I would like to mention that I have been improving not only my marks but also my deep knowledge in the subjects during my time at university. This is due to several reasons. First of all, I consider myself a very hard-working person as well as highly competitive in all aspects. These competences have given me the power to become better in many aspects of my life, specially in Math in which the fact of having bright classmates has encouraged me to do better in many subjects. On the other hand, the annual participation in many well-known Math and Physics competitions proves my absolute love for these subjects as well as the passion they transmit to myself. All of this academic background stands me in good stead to pursue higher studies abroad.


  % On balance, the acceptance in this PhD program would allow me to continue expanding my knowledge of Math more deeply at the so prestigious \uni.

  % Thank you very much for considering my application.
  % \bigskip

  % Yours faithfully,

  % Víctor Ballester

  I am writing to express my sincere interest in a \program\ at \uni. My name is Víctor Ballester, and I am currently enrolled in the M2 Applied and Theoretical Mathematics program at Paris-Dauphine University, following my graduation from Mathematics at the Autonomous University of Barcelona last summer. I am particularly attracted to the field of Applied Mathematics, with a specific focus on computational PDEs, Numerical Analysis, and recently, Fluid Dynamics.

  % The area of fluid dynamics, particularly Aerodynamics, has captured my attention due to its theoretical and numerical complexities. I aspire to contribute to research in this field, exploring both the theoretical foundations and numerical methods. This motivation is one of the primary reasons for my application to a \program\ at \uni.

  The area of fluid dynamics, particularly Aerodynamics, has captured my attention due to its theoretical and numerical complexities. I aspire to contribute to research in this field, exploring both the theoretical foundations and numerical methods. This motivation is one of the primary reasons for my application to a \program\ at \uni.


  There are two key reasons why I am seeking admission to this Ph.D.\ program. Firstly, my undergraduate and current graduate studies have equipped me with a strong foundation in analysis, numerical methods and the theory of differential equations. Courses such as Differential Equations and Modelling (I and II), Numerical Methods, and Partial Differential Equations have provided me with the necessary tools to tackle complex applied problems across various scientific disciplines. Moreover, in my master studies, I have been able to delve deeper into Fluid Dynamics and Turbulence, which is something I would like to continue exploring in my Ph.D.\ studies.
  I find the intersection of Mathematics with Physics and Engineering to be highly intriguing, as it allows for rigorous exploration while addressing practical challenges.

  Secondly, getting to study at an excellent institution with renowned professors is a thrilling challenge for me. I have always wanted to do advanced research in another country, and this chance really motivates and excites me. Also, living and studying in a different country is enriching from a cultural perspective. Therefore, I am really looking forward to the idea of moving to \city\ for my studies.

  Regarding my academic performance in Mathematics, I have consistently strived for improvement throughout my university years. My dedication and competitiveness have driven me to excel in various aspects of my life, especially in Mathematics. The presence of talented classmates has further encouraged my personal growth in these subjects. Furthermore, my active participation in renowned Mathematics and Physics competitions each year underscores my genuine passion for these fields and the knowledge they impart. I believe this academic background positions me well to pursue advanced studies abroad.

  % My primary research groups of interest at \uni\ are the \emph{Nonlinear Dynamics and Turbulence} group, lead by Prof.\ Björn Hof, and the \emph{Theory of Partial Differential Equations, Applied and Numerical Analysis} group, lead by Prof.\ Julian Fischer. Moreover, as the application form requires, I would like to spend my first year at \uni\ also in the \emph{Emergent Electronic Phenomena in 2D Materials} group, \emph{Computational soft and living matter} group or the \emph{Computational materials science} group, to gain a broader perspective on the field of computational physics.

  In conclusion, being accepted into this Ph.D.\ program would enable me to deepen my understanding of Aerodynamics at \uni. I am confident that this program will provide me with the necessary tools to expand my knowledge and contribute meaningfully to the academic community.

  Thank you for considering my application.
  \bigskip

  Yours faithfully,

  Víctor Ballester

\end{letter}
\end{document}
