 
% sample of a latex file
\documentclass[11pt]{letter}
\usepackage[utf8]{inputenc}
% \usepackage[margin=1in]{geometry}

% THIS IS A COVER LETTER
\begin{document}
\thispagestyle{empty}
Dear Aston Martin F1 Team,

I am writing to express my enthusiasm for your student placement position. As a recent graduate of the Autonomous University of Barcelona with a degree in Mathematics and currently pursuing a master's degree in Applied Mathematics at Paris-Dauphine University, with a specialization in fluid dynamics, I am eager to bring my passion and skills to your team.

Throughout my academic journey, I have discovered a deep-seated passion for applied mathematics, particularly in the realm of aerodynamics. This passion manifests both in my theoretical approach, where I endeavor to model fluid flow, and in my proficiency in computational methods, where I design algorithms to integrate the equations of dynamics. My programming skills have allowed me to excel in this aspect of my work, and I am constantly motivated to expand my proficiency in various programming languages.

I am a dedicated and driven individual who thrives on taking on new challenges. I consider myself a fast learner, always eager to acquire new knowledge and skills. These qualities have enabled me to achieve my academic and personal goals in the past. While I understand that the student placement typically targets undergraduate students, I believe my passion for Applied Mathematics and Engineering will prove to be an asset to your team. This opportunity would be a pivotal moment in my career, affording me the chance to delve into the world of car racing and apply my expertise.

In conclusion, securing this position with your team would be a dream come true for me. It would provide me with the ideal platform to put my knowledge to practical use in cutting-edge technology while learning from some of the world's most accomplished engineers. I am confident that my dedication, skills and knowledge will contribute positively to the success of the Aston Martin F1 Team.

Thank you for considering my application. I eagerly anticipate the opportunity to discuss how I can make a meaningful contribution to the Aston Martin F1 Team.

Sincerely,

Víctor
\end{document}
Dear Aston Martin F1 Team,

I am writing to express my utmost enthusiasm and deep interest in the opportunity to join the Aston Martin F1 Team for a student placement. Although I have already graduated, I firmly believe that my passion, skills, and strong work ethic make me an ideal candidate for this role. I am eager to contribute my expertise in computational mathematics, fluid dynamics, CFD (Computational Fluid Dynamics), and programming languages to the team while immersing myself in the exciting world of Formula 1 racing.

Throughout my academic journey, I have developed a competitive spirit and a relentless drive to excel. My studies provided me with a solid foundation in computational mathematics, fluid dynamics, and CFD, enabling me to understand the intricate mathematical principles governing fluid flow and its simulation. I have consistently exhibited a strong work ethic and an unwavering commitment to achieving excellence in every endeavor.

My passion for mathematical sciences has been a driving force throughout my academic and professional pursuits. I have dedicated significant time and effort improving my programming skills in many languages such as Python, MATLAB, and C++, enabling me to develop efficient algorithms for numerical simulations and extract valuable insights from it.

Joining the Aston Martin F1 Team would be a dream come true for me. The opportunity to collaborate with industry experts, explore cutting-edge technologies, and contribute to the development of high-performance race cars is incredibly inspiring. I am confident that my knowledge, skills, and dedication will enable me to make a meaningful impact on the team's success.

I possess a competitive spirit in the best sense of the term. I thrive in fast-paced, dynamic environments and possess a tenacious drive to push boundaries and achieve exceptional results. I approach challenges with a positive mindset, embracing them as opportunities to learn and grow. As a hard-working individual, I am committed to investing the necessary time and effort to excel in my role and contribute to the team's goals.

Despite not being an undergraduate, I assure you that I will not disappoint. My previous academic achievements and professional experiences have honed my ability to adapt quickly, collaborate effectively, and deliver high-quality work. I am confident in my capacity to integrate seamlessly into the team and bring a fresh perspective and valuable skills to the table.

Thank you for considering my application. I look forward to the opportunity to discuss how I can contribute to the Aston Martin F1 Team.

Yours sincerely,

Víctor