 
% sample of a latex file
\documentclass[11pt]{letter}
\usepackage[utf8]{inputenc}
% \usepackage[margin=1in]{geometry}

\newcommand{\teamname}{McLaren Racing Team}

% THIS IS A COVER LETTER
\begin{document}
\thispagestyle{empty}
Dear \teamname,

I am writing to express my enthusiasm for your placement position. As a recent graduate of the Autonomous University of Barcelona with a degree in Mathematics, I am currently pursuing a master's degree in Applied Mathematics at Paris-Dauphine University, specializing in computational fluid dynamics. I am eager to bring my passion and skills to your team.

% and currently pursuing a master's degree in Applied Mathematics at Paris-Dauphine University, specializing in fluid dynamics, I am eager to bring my passion and skills to your team.

Throughout my academic journey, I have developed a profound interest in Applied Mathematics, particularly in the field of Aerodynamics. This interest encompasses both theoretical approaches, where I strive to model fluid flow, and computational methods, where I design algorithms to incorporate into the equations. My proficiency in programming has allowed me to excel in these areas, and I am consistently motivated to enhance my skills in various programming languages.

I am a dedicated and determined individual who thrives on embracing new challenges. I consider myself a quick learner, always eager to acquire new knowledge and skills. These qualities have propelled me towards achieving my academic and personal goals in the past. I firmly believe that my passion for Applied Mathematics and Engineering will prove to be a valuable asset to your team. Securing this opportunity would be a pivotal moment in my career, offering me the chance to immerse myself in the world of car racing and apply my expertise.

In conclusion, joining your team would be a dream come true for me. It would provide me with an ideal platform to apply my knowledge in cutting-edge technology while learning from some of the industry's most accomplished engineers. I am confident that my dedication, skills, and knowledge will contribute positively to the success of the \teamname.

Thank you for considering my application. I eagerly anticipate the opportunity to discuss how can I make a meaningful contribution to the \teamname.

Sincerely,

Víctor Ballester
\end{document}
Regarding my current notice period, I am flexible and open to discussing suitable arrangements. Starting from July or August 2024, I would be available to join the team. However, if there is an opportunity to align my research master thesis with any ongoing experiments or projects at your organization, I may be able to commence earlier. I am willing to explore possibilities and find a mutually beneficial arrangement that accommodates both my academic commitments and the requirements of the role.

Given that this would be my first professional experience in a company, I don't have a specific salary figure in mind. However, I would anticipate a salary in the range of at least 2000€ per month. Please note that these numbers are tentative, and I am open to discussing and negotiating a fair compensation package based on the responsibilities, requirements, and market standards associated with the role.

As a recent graduate, I am seeking a new position to kick-start my career and apply the knowledge and skills I have acquired during my academic journey. I am excited to transition from the theoretical realm of academia to the practical world of motorsports. I believe that securing a position with Williams Racing would provide me with the opportunity to combine my passion for applied mathematics and fluid dynamics with the thrilling challenges of car racing. I am eager to contribute my expertise to a dynamic and innovative team like Williams Racing.

I want to work at Williams Racing because of the team's rich history, strong reputation, and commitment to excellence in Formula One. Williams Racing has a long-standing tradition of success and a track record of nurturing talent, both in terms of drivers and engineers. Being part of such a renowned team would not only be a tremendous honor but also a fantastic learning opportunity for me.